From heartbeat to data – Using wearable fitness trackers as an affordable approach to assess teacher stress

### 2024-09-18 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
appendix angefangen

>>>>

```{r plots_appendix, include=FALSE}
mods <-   
  df_regression %>% 
  split(.$time_span) %>% 
  map(~ lm(formula = heart_rate_std ~ 0 + ID + time:ID,
       data = .
       )
      )

graph_data <- 
  df_regression %>% 
  split(.$time_span)

example <- list(mod = mods$preparation, data = graph_data$preparation)

plot_list_appendix <- list(
  `Preparation Phase` = list(name = "Pre-Teaching Interval", mod = mods$preparation, data = graph_data$preparation),
     `Teaching Phase` = list(name = "Teaching Interval", mod = mods$teaching, data = graph_data$teaching),
     `Post Teaching Phase` = list(name = "Post-Teaching Interval",mod = mods$post, data = graph_data$post),
     `Interview Phase` = list(name = "Interview Interval",mod = mods$interview, data = graph_data$interview),
     `End Phase` = list(name = "End Interval",mod = mods$end, data = graph_data$end)
     ) %>% 
  map(~ ggplot(data = .$data,
               mapping = aes(x = time,
                             y = heart_rate_std,
                             group = ID)) +
        geom_line(mapping = aes(y = fitted(.$mod)),
                  color = "blue",
                  size = 1) +
        geom_point(alpha = 0.5,
                   size = 0.5) +
        scale_x_continuous(breaks = c(0, 5, 10)) +
        labs(title = .$name,
             y = "Heart Rate (Standardized)",
             x = "Time (in Seconds)") +
        facet_wrap( ~ ID, nrow = 6) +
        theme_apa()
      )

preparation_plot <- plot_list_appendix$`Preparation Phase`

teaching_plot <- plot_list_appendix$`Teaching Phase`

post_teaching_plot <- plot_list_appendix$`Post Teaching Phase`

interview_plot <- plot_list_appendix$`Interview Phase`

end_plot <- plot_list_appendix$`End Phase`

ggsave(preparation_plot,
       filename = "plots_publication/plot_preparation_appendix.pdf",
       width = 25,
       height = 25,
       units = "cm")

ggsave(teaching_plot,
       filename = "plots_publication/plot_teaching_appendix.pdf",
       width = 15,
       height = 25,
       units = "cm")

ggsave(post_teaching_plot,
       filename = "plots_publication/plot_post_teaching_appendix.pdf",
       width = 20,
       height = 12,
       units = "cm")

ggsave(interview_plot,
       filename = "plots_publication/plot_interview_appendix.pdf",
       width = 20,
       height = 12,
       units = "cm")

ggsave(end_plot,
       filename = "plots_publication/plot_end_appendix.pdf",
       width = 20,
       height = 12,
       units = "cm")

```{=latex}
\newpage
\appendix
\section*{Appendix}

\setcounter{figure}{0}  % Reset figure numbering

\renewcommand{\thefigure}{A\arabic{figure}}  % Figures labeled A1, A2, etc.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.7\textwidth]{appendix_figure1.png}
  \caption{Laboratory setting of the micro-teaching unit. Note. The setting included three actors as the class (left) and a teacher (participant, right).}
  \label{micro-teaching}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.7\textwidth]{appendix_figure2.png}
  \caption{Laboratory setting of the interview. Note. The experimenter and participant watched the previously taught micro-teaching unit on video.}
  \label{laboratory}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/plot_preparation_appendix.pdf}
  \caption{bla..}
  \label{preparation}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/plot_teaching_appendix.pdf}
  \caption{bla..}
  \label{teaching}
\end{figure}
```
